%=============================================================================
% BIBLIOGRAPHIE
%=============================================================================
\chapter*{Bibliographie}
\addcontentsline{toc}{chapter}{Bibliographie}

\section*{Publications Académiques}

\begin{thebibliography}{99}

\subsection*{Maintenance Prédictive et RUL}

\bibitem{cmapss2008}
Saxena, A., Goebel, K., Simon, D., \& Eklund, N. (2008).
\textit{Damage propagation modeling for aircraft engine run-to-failure simulation}.
IEEE International Conference on Prognostics and Health Management (PHM), pp. 1-9.
DOI: 10.1109/PHM.2008.4711414

\bibitem{lei2018}
Lei, Y., Li, N., Guo, L., Li, N., Yan, T., \& Lin, J. (2018).
\textit{Machinery health prognostics: A systematic review from data acquisition to RUL prediction}.
Mechanical Systems and Signal Processing, 104, pp. 799-834.
DOI: 10.1016/j.ymssp.2017.11.016

\bibitem{ran2019}
Ran, Y., Zhou, X., Lin, P., Wen, Y., \& Deng, R. (2019).
\textit{A survey of predictive maintenance: Systems, purposes and approaches}.
arXiv preprint arXiv:1912.07383.

\bibitem{carvalho2019}
Carvalho, T. P., Soares, F. A., Vita, R., Francisco, R. D. P., Basto, J. P., \& Alcalá, S. G. (2019).
\textit{A systematic literature review of machine learning methods applied to predictive maintenance}.
Computers \& Industrial Engineering, 137, 106024.
DOI: 10.1016/j.cie.2019.106024

\subsection*{Deep Learning pour Séries Temporelles}

\bibitem{lstm1997}
Hochreiter, S., \& Schmidhuber, J. (1997).
\textit{Long short-term memory}.
Neural Computation, 9(8), pp. 1735-1780.
DOI: 10.1162/neco.1997.9.8.1735

\bibitem{zheng2017}
Zheng, S., Ristovski, K., Farahat, A., \& Gupta, C. (2017).
\textit{Long Short-Term Memory Network for Remaining Useful Life estimation}.
IEEE International Conference on Prognostics and Health Management (ICPHM), pp. 88-95.
DOI: 10.1109/ICPHM.2017.7998311

\bibitem{zhao2019}
Zhao, R., Yan, R., Wang, J., \& Mao, K. (2019).
\textit{Learning to monitor machine health with convolutional bi-directional LSTM networks}.
Sensors, 17(2), 273.
DOI: 10.3390/s17020273

\bibitem{li2018}
Li, X., Ding, Q., \& Sun, J. Q. (2018).
\textit{Remaining useful life estimation in prognostics using deep convolution neural networks}.
Reliability Engineering \& System Safety, 172, pp. 1-11.
DOI: 10.1016/j.ress.2017.11.021

\subsection*{Détection d'Anomalies}

\bibitem{liu2008}
Liu, F. T., Ting, K. M., \& Zhou, Z. H. (2008).
\textit{Isolation forest}.
IEEE International Conference on Data Mining (ICDM), pp. 413-422.
DOI: 10.1109/ICDM.2008.17

\bibitem{chalapathy2019}
Chalapathy, R., \& Chawla, S. (2019).
\textit{Deep learning for anomaly detection: A survey}.
arXiv preprint arXiv:1901.03407.

\bibitem{chandola2009}
Chandola, V., Banerjee, A., \& Kumar, V. (2009).
\textit{Anomaly detection: A survey}.
ACM Computing Surveys (CSUR), 41(3), pp. 1-58.
DOI: 10.1145/1541880.1541882

\subsection*{Architectures Microservices et Event-Driven}

\bibitem{newman2015}
Newman, S. (2015).
\textit{Building Microservices: Designing Fine-Grained Systems}.
O'Reilly Media. ISBN: 978-1491950357

\bibitem{richardson2018}
Richardson, C. (2018).
\textit{Microservices Patterns: With examples in Java}.
Manning Publications. ISBN: 978-1617294549

\bibitem{fowler2014}
Fowler, M., \& Lewis, J. (2014).
\textit{Microservices: a definition of this new architectural term}.
martinfowler.com/articles/microservices.html

\bibitem{stopford2018}
Stopford, B. (2018).
\textit{Designing Event-Driven Systems: Concepts and Patterns for Streaming Services with Apache Kafka}.
O'Reilly Media. ISBN: 978-1492038221

\subsection*{Apache Kafka et Streaming}

\bibitem{kafka2011}
Kreps, J., Narkhede, N., \& Rao, J. (2011).
\textit{Kafka: A distributed messaging system for log processing}.
Proceedings of the NetDB, pp. 1-7.

\bibitem{narkhede2017}
Narkhede, N., Shapira, G., \& Palino, T. (2017).
\textit{Kafka: The Definitive Guide: Real-Time Data and Stream Processing at Scale}.
O'Reilly Media. ISBN: 978-1491936160

\bibitem{kleppmann2017}
Kleppmann, M. (2017).
\textit{Designing Data-Intensive Applications: The Big Ideas Behind Reliable, Scalable, and Maintainable Systems}.
O'Reilly Media. ISBN: 978-1449373320

\subsection*{MLOps et DevOps}

\bibitem{zaharia2018}
Zaharia, M., Chen, A., Davidson, A., Ghodsi, A., Hong, S. A., Konwinski, A., ... \& Stoica, I. (2018).
\textit{Accelerating the machine learning lifecycle with MLflow}.
IEEE Data Engineering Bulletin, 41(4), pp. 39-45.

\bibitem{sculley2015}
Sculley, D., Holt, G., Golovin, D., Davydov, E., Phillips, T., Ebner, D., ... \& Dennison, D. (2015).
\textit{Hidden technical debt in machine learning systems}.
Advances in Neural Information Processing Systems (NeurIPS), pp. 2503-2511.

\bibitem{kim2016}
Kim, G., Humble, J., Debois, P., \& Willis, J. (2016).
\textit{The DevOps Handbook: How to Create World-Class Agility, Reliability, and Security in Technology Organizations}.
IT Revolution Press. ISBN: 978-1942788003

\bibitem{forsgren2018}
Forsgren, N., Humble, J., \& Kim, G. (2018).
\textit{Accelerate: The Science of Lean Software and DevOps: Building and Scaling High Performing Technology Organizations}.
IT Revolution Press. ISBN: 978-1942788331

\subsection*{Protocoles IIoT}

\bibitem{opcua2017}
Mahnke, W., Leitner, S. H., \& Damm, M. (2009).
\textit{OPC Unified Architecture}.
Springer Science \& Business Media. ISBN: 978-3540688983

\bibitem{mqtt2014}
Banks, A., \& Gupta, R. (2014).
\textit{MQTT Version 3.1.1}.
OASIS standard. Available at: http://docs.oasis-open.org/mqtt/mqtt/v3.1.1/

\bibitem{modbus2012}
Modbus Organization. (2012).
\textit{Modbus Application Protocol Specification V1.1b3}.
Available at: www.modbus.org

\subsection*{Bases de Données Time-Series}

\bibitem{timescaledb2017}
Freedman, M., Beimel, Y., \& Askary, N. (2017).
\textit{TimescaleDB: Fast and Scalable Timeseries}.
Technical report, Timescale, Inc.

\bibitem{dunning2014}
Dunning, T., \& Friedman, E. (2014).
\textit{Time Series Databases: New Ways to Store and Access Data}.
O'Reilly Media. ISBN: 978-1491914724

\subsection*{Observabilité et Monitoring}

\bibitem{prometheus2016}
Volz, J., \& Rabenstein, B. (2016).
\textit{Prometheus: Up \& Running: Infrastructure and Application Performance Monitoring}.
O'Reilly Media. ISBN: 978-1492034148

\bibitem{jaeger2017}
Shkuro, Y. (2019).
\textit{Mastering Distributed Tracing: Analyzing performance in microservices and complex systems}.
Packt Publishing. ISBN: 978-1788628464

\bibitem{beyer2016}
Beyer, B., Jones, C., Petoff, J., \& Murphy, N. R. (2016).
\textit{Site Reliability Engineering: How Google Runs Production Systems}.
O'Reilly Media. ISBN: 978-1491929124

\subsection*{Sécurité et Standards}

\bibitem{iec62443}
International Electrotechnical Commission. (2018).
\textit{IEC 62443: Security for industrial automation and control systems}.
IEC Standard Series.

\bibitem{nist2018}
National Institute of Standards and Technology. (2018).
\textit{Framework for Improving Critical Infrastructure Cybersecurity, Version 1.1}.
NIST Cybersecurity Framework.

\subsection*{Industrie 4.0}

\bibitem{kagermann2013}
Kagermann, H., Wahlster, W., \& Helbig, J. (2013).
\textit{Recommendations for implementing the strategic initiative INDUSTRIE 4.0}.
Final report of the Industrie 4.0 Working Group, Forschungsunion.

\bibitem{liao2017}
Liao, Y., Deschamps, F., Loures, E. D. F. R., \& Ramos, L. F. P. (2017).
\textit{Past, present and future of Industry 4.0-a systematic literature review and research agenda proposal}.
International Journal of Production Research, 55(12), pp. 3609-3629.
DOI: 10.1080/00207543.2017.1308576

\end{thebibliography}

\section*{Ressources en Ligne et Documentation Technique}

\begin{itemize}
    \item \textbf{Apache Kafka Documentation}. \url{https://kafka.apache.org/documentation/}
    \item \textbf{PyTorch Documentation}. \url{https://pytorch.org/docs/}
    \item \textbf{FastAPI Documentation}. \url{https://fastapi.tiangolo.com/}
    \item \textbf{Kubernetes Documentation}. \url{https://kubernetes.io/docs/}
    \item \textbf{MLflow Documentation}. \url{https://mlflow.org/docs/}
    \item \textbf{TimescaleDB Documentation}. \url{https://docs.timescale.com/}
    \item \textbf{Prometheus Documentation}. \url{https://prometheus.io/docs/}
    \item \textbf{Grafana Documentation}. \url{https://grafana.com/docs/}
    \item \textbf{OPC Foundation}. \url{https://opcfoundation.org/}
    \item \textbf{NASA Prognostics Data Repository}. \url{https://ti.arc.nasa.gov/tech/dash/groups/pcoe/prognostic-data-repository/}
\end{itemize}
